Fastest Paths Between Points in $\R^2$ for a Particle Moving with Constant Speed and Bounded Centripetal Acceleration

### 2013-10-11 fixed_speed_theorems.tex
Added paper.pdf.

Now let us introduce a particle $p_2$ with the same conditions as $p_1$, except that at some time $t_b < t_s$, $p_2$ will have $a_{c,2}(t) \neq \bar{a}_c$. We shall show that the fastest path for $p_2$, $\hat{\gamma_2(t)}$, after this divergence is strictly slower than the fastest path for $p_1$, $\hat{\gamma}_1$, which will allow us to conclude that $\gamma_1(t)$ is the unique fastest path.

We can examine the difference in $r$ and $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conj:optimal-position} to finish our proof. Recall equations \ref{eq:r-diff-2} and \ref{eq:theta-diff} which we derived in a previous section. We can use equation \ref{eq:r-diff-2} to obtain the following:

>>>>

Now let us introduce a particle $p_2$ with the same conditions as $p_1$, except that $a_{c,2}(t) < \bar{a}_c$ for some time interval $t \in [t_a, t_b], [t_a, t_b] < t_s$. We shall show that the fastest path for $p_2$, $\hat{\gamma_2(t)}$, after $t_b$ is strictly worse than the fastest path for $p_1$, $\hat{\gamma}_1$, which will allow us to conclude that $\gamma_1(t)$ is the unique fastest path.

We will first prove that $r_1(t_b) < r_2(t_b)$ and $\theta_1(t_b) < \theta_2(t_b)$ and then invoke Conjecture \ref{conj:optimal-position} to finish our proof. Recall equations \ref{eq:r-diff-2} and \ref{eq:theta-diff} which we derived in a previous section. We can use equation \ref{eq:r-diff-2} to obtain the following:

### 2013-10-11 particle_definitions.tex
Added paper.pdf.

  \[a_t(t) \coloneqq \frac{dv(t)}{dt}\]
\end{definition}
% -----------------------------------------------------------------------------

@@

The proof of the lemma in the case where $a_t(t)$ is nonzero is nearly identical, since the component of $\bvec{dv(t)}$ in the direction $\bhat{v}(t)$ is negligible compared to $v(t)$.

>>>>

  \begin{equation}
    a_t(t) \coloneqq \frac{dv(t)}{dt}
  \end{equation}
\end{definition}
% -----------------------------------------------------------------------------

@@

The proof of the lemma in the case where $a_t(t)$ is nonzero is nearly identical, since the component of $\bvec{dv}(t)$ in the direction $\bhat{v}(t)$ is negligible compared to $v(t)$.
